Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-08 paper/main.tex
[issue 2.21] remove tpc core hours

We note that TPC is able to utilize parallelization, and parallelized on 64
cores of Xeon E5 2.7 GHz processors, it takes 23 minutes to train 500 trees,
for a total of 25 CPU hours.

>>>>

\sout{
We note that TPC is able to utilize parallelization, and parallelized on 64
cores of Xeon E5 2.7 GHz processors, it takes 23 minutes to train 500 trees,
for a total of 25 CPU hours.
}
